---
title: "Sediment Oxygen Consumption"
author: "Chih-Lin Wei"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```


Obtain the initial and 85% of the initial DO concentration
---

```{r}
library(ggplot2)
library(doBy)
library(reshape2)
library(scales)
library(plyr)
library(readxl)
library(knitr)
library(TWBathyMap)

# dark theme for ggplot
dark <- theme(plot.background = element_rect(colour = 'NA', fill = 'gray10'),
        panel.background = element_rect(colour = 'NA', fill = 'transparent'),
        legend.background = element_rect(colour = 'NA', fill = 'transparent'),
        legend.title = element_text(colour = 'white'),
        legend.text = element_text(colour = 'white'),
        axis.title = element_text(colour = 'white'),
        axis.text = element_text(colour = 'white'),
        axis.ticks = element_line(colour = 'white'),
        panel.border = element_rect(fill = 'NA', colour = 'white'), 
        panel.grid.major = element_line(colour = 'gray30'),
        panel.grid.minor = element_line(colour = 'gray20'))

# Load data
ic <- read_excel("../GPSC_data/GPSC_incubation/GPSC_incubation_2021.12.29.xlsx", sheet=1)
ic <- ic[!is.na(ic$DO),]
ic <- ic[-grep("Bad", ic$Comment),]

# Remove OR1_1126 GC1, GS3, GS4 because it's show very large flux and only based on 2 points
# Remove OR1_1114 GC1 because it's show extremely large flux
# Remove OR1_1151 because it's show extremely low faunal abundance
bad1 <- with(ic, Cruise=="OR1_1114" & Station=="GC1")
bad2 <- with(ic, Cruise=="OR1_1126" & (Station=="GC1"|Station=="GS3"|Station=="GS4"))
#bad3 <- with(ic, Cruise=="OR1_1151")
water <- with(ic, Sample=="W")
ic <- ic[!(bad1|bad2|water), ]

ic$DateTime <- as.POSIXct(paste(ic$Date, ic$Time, sep=" "), tz="Asia/Taipei")
ic$Region <- factor(ic$Station)
levels(ic$Region) <- c(rep("Fangliao", 7), rep("Gaoping", 13), rep("Kaohsiung", 2), rep("Gaoping", 9), rep("Kaohsiung", 2), rep("Dongsha", 2), rep("Taiping", 2))

# Initial concentration and 85% of intial concentration for sediment incubation
in_conc <- splitBy(~Cruise+Station+Deployment+Tube, as.data.frame(ic))
in_conc <- lapply(in_conc, FUN=function(x){
  Cruise <- x$Cruise[1]
  Station <- x$Station[1]
  Deployment <- x$Deployment[1]
  Tube <- x$Tube[1]
  Habitat <- x$Habitat[1]
  Initial <- x$DO[1]
  LL85 <- x$DO[1]*0.85
  data.frame(Cruise, Station, Deployment, Tube, Habitat, Initial, LL85)
  })
in_conc <- do.call(rbind, in_conc)
```

```{r, fig.width=8, fig.height=6}
library(swtmap)
library(maptools)
library(raster)

loc <- read_excel("../GPSC_data/GPSC_macro_sorting/GPSC_macro_sorting_2021.11.23.xlsx", sheet=1)
all <- summaryBy(Longitude+Latitude+Depth~Station+Habitat, data=as.data.frame(loc), FUN=mean, keep.names=TRUE)
loc <- all[match(unique(ic$Station), all$Station),]
coordinates(loc) <- c("Longitude", "Latitude")
projection(loc) <- projection(bathy)

e <- extent(119.8, 120.9, 21.6, 22.6)
r <- crop(bathy, e)
iso200<- rasterToContour(r, levels=-200)
iso1000<- rasterToContour(r, levels=c(-3000, -2000, -1000, 0))
extra <- function(...){
         panel.levelplot.raster(...)
         sp.lines(iso200, col="gray30", lty=2)
         sp.lines(iso1000, col="gray30")
         sp.points(loc, cex=1.5, pch=21, fill=c("black", "white")[factor(loc$Habitat)], col="black")
         sp.pointLabel(loc, labels=loc$Station)
         SpatialPolygonsRescale(layout.scale.bar(), offset=c(120.6, 21.65), scale = 30/(111.321*cos(21.65*pi/180)), fill = c("white","black"), col = "black")
         sp.text(loc = c(120.62, 21.68), "0")
         sp.text(loc = c(120.85, 21.68), "30 km")
}

tbspplot(r, panel=extra)
```


Linear regression between DO and time
---
- Dashed line: 85% DO of the initial concentration
- Close symbol: Sediment incubation
- Open symbol: Bottom water incubation

```{r, fig.width=10, fig.height=8}
do_ls<-splitBy(~Cruise+Station+Deployment+Tube, as.data.frame(ic))
do_ls<-lapply(do_ls, FUN=function(x){
  x$Elapse <- (x$DateTime-min(x$DateTime))/3600
  return(x)
  })
ic <- ldply(do_ls, rbind)

flux_fun <- function(x){
  fit <- lm(DO~Elapse, x)
  oxy <- fit$coefficient[2]*24 # mmol/L/day
  vol <- (x$Height[1]*5.25^2*pi)/1000 # L
  are <- 5.25^2*pi/10000 # m2
  DO_flux <- oxy*vol/are/1000 # mmol/m2/d
  a <- fit$coefficient[1]
  b <- fit$coefficient[2]
  P <- summary(fit)$coefficient[2,4]
  Date <- x$Date[1]
  Habitat <- x$Habitat[1]
  Region <- x$Region[1]
  Depth <- x$Depth[1]
  Cruise <- x$Cruise[1]
  Station <- x$Station[1]
  Deployment <- x$Deployment[1] 
  Tube <- x$Tube[1]
  Sample <- x$Sample[1]
  Incubator <- x$Incubator[1]
  Temperature <- mean(x$Temperature)
  data.frame(Cruise, Date, Habitat, Region, Depth, Station, Deployment, Tube, Sample, Incubator, a, b, P, DO_flux, Temperature)
}

do_fx <- lapply(do_ls, FUN=flux_fun)
do_fx<-do.call(rbind, do_fx)

lev <- c("SC2", "SC3","KS1", "KS3",
         "GC1", "GC2", "GC3", "GC4", "GC5", "GC6",
         "S1", "S2", "S3", "S4", "S5", "S6", "S7", "GS1", "GS2", "GS3", "GS4", "GS5", "GS6", "GS7", "M1", "L1",
         "FC1", "FC2", "FC4", "FC5A","FS1", "FS2", "FS5C",
         "ST1", "ST3", "ST5", "ST5-2")

do_fx$Station <- factor(do_fx$Station, levels=lev)
ic$Station <- factor(ic$Station, levels = lev)

# DO as function of time
ggplot(data=ic, aes(x=Elapse, y=DO, colour=Cruise))+
  #geom_hline(data=in_conc, aes(yintercept=LL85, colour=Cruise), lty=2)+
  geom_point()+
  scale_shape_manual(values=c(19,1))+
  geom_abline(data=do_fx, aes(intercept=a, slope=b, colour=Cruise))+
  facet_wrap(~Station, scale="free")+
  xlab("Incubation time (hour)")+
  ylab(expression(Dissolved~ooxygen~concentration(mu~mol/L)))+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) #%+replace% dark
```

Apply Q10 (=2, Valiela, 1995) adjustment with in-situ CTD data
---
```{r}
# In-situ temperature from CTD
ctd <- read_excel("../GPSC_data/GPSC_CTD/GPSC_CTD_2021.12.29.xlsx", sheet=1)
ctd <- splitBy(~Cruise+Station, as.data.frame(ctd))

# Function to get average of bottom 3 deepest CTD data
deep_fun <- function(x) {
   dat <- x[order(x$pressure, decreasing=TRUE)[1:3],]
   summaryBy(.~Cruise+Station, data=dat, keep.names=TRUE, na.rm=TRUE)
}
ctd <- lapply(ctd, FUN=deep_fun)
ctd <- ldply(ctd)[, -1]

# Average temperature
ctd$Temperature <- rowMeans(ctd[, c("temperature_T1", "temperature_T2")], na.rm=TRUE)
id1 <- with(do_fx, paste(Cruise, Station))
id2 <- with(ctd, paste(Cruise, Station))

# Set OR1_1190 GS6 temperature to the temperature measured during OR1 1169
id1[is.na(match(id1, id2))] <- c("OR1_1169 GS6")
do_fx$In_situ_temperature <- ctd[match(id1, id2), "Temperature"]

# Q10 function
q10_fun <- function(t1, t2, r1, q10){
  a <- 10/(t1-t2)
  r1/(q10^(1/a))
}

do_fx$In_situ_DO_flux <- q10_fun(t1=do_fx$Temperature, t2=do_fx$In_situ_temperature, r1=do_fx$DO_flux, q10=2)
```

In-situ oxygen flux by core replications
```{r}
# Fit a log-linear model
f <- lm(log10(-In_situ_DO_flux)~Depth*Habitat*Region, data=subset(do_fx, !(Region=="Dongsha"|Region=="Taiping")))
summary(f)
anova(f)

ls <- splitBy(~Habitat, data=do_fx)
f<-lapply(ls, FUN=function(x)lm(log10(-In_situ_DO_flux)~Depth, data=x))
lapply(f, FUN=summary)
nd <- lapply(ls, FUN=function(x){
  out <- as.data.frame(seq(min(x$Depth), max(x$Depth)))
  names(out) <- "Depth"
  return(out)
})

fnd <- list(Canyon=list(f=f[[1]], nd=nd[[1]]), Slope=list(f=f[[2]], nd=nd[[2]]))
pred <- lapply(fnd, FUN=function(x)cbind(x$nd, -10^predict(x$f, x$nd, interval="confidence")))
pred <- ldply(pred, rbind)
names(pred)[1] <- "Habitat"

ggplot(data=do_fx, 
             aes(x = Depth, y = In_situ_DO_flux))+
  geom_point(aes(colour=Habitat, shape=Region), size=3)+
  scale_shape_manual(values=c(19, 3, 4, 1, 0))+
  geom_line(data=pred, aes(x=Depth, y=fit, colour=Habitat))+
  geom_ribbon(data=pred, aes(x=Depth, y=fit, ymin=lwr, ymax=upr, fill=Habitat), alpha=0.2)+
  facet_wrap(~Habitat, scale="free")+
  xlab("Depth (m)")+
  ylab(expression(Oyxgen~flux~(mmol~m^-2~day^-1)))+
  theme_bw() #%+replace% dark

ggplot(data=do_fx, 
             aes(x = Depth, y = -In_situ_DO_flux))+
  geom_point(aes(colour=Habitat, shape=Region), size=3)+
  scale_shape_manual(values=c(19, 3, 4, 1, 0))+
  scale_y_log10()+
  stat_smooth(method="lm", formula=y~x, alpha=0.2, aes(colour=Habitat, fill=Habitat))+
  facet_wrap(~Habitat, scale="free")+
  xlab("Depth (m)")+
  ylab(expression(Total~Oxygen~Utilization~(mmol~m^-2~day^-1)))+
  theme_bw() #%+replace% dark

ggplot(data=do_fx, 
             aes(x = Depth, y = -In_situ_DO_flux))+
  geom_point(aes(colour=Habitat, shape=Region), size=3)+
  scale_shape_manual(values=c(19, 3, 4, 1, 0))+
  scale_y_log10()+
  stat_smooth(method="lm", formula=y~x, alpha=0.2, colour="gray")+
  xlab("Depth (m)")+
  ylab(expression(Total~Oxygen~Utilization~(mmol~m^-2~day^-1)))+
  theme_bw() #%+replace% dark

or <- with(do_fx, 
           order(Sample, Cruise, Station, Deployment))
#write.csv(do_fx[or,], file="../GPSC_data/GPSC_incubation/GPSC_TOU.csv", row.names=F, na = "")
#write.csv(summaryBy(DO_flux+In_situ_DO_flux~Cruise+Station, data=do_fx[or,], FUN=c(mean, sd, length)), file="../GPSC_data/GPSC_incubation/GPSC_TOU_st.csv", row.names=F, na = "")
```

Average in-situ Oxygen flux by cruise and station
---
```{r}
do_fx_summary <- summaryBy(In_situ_DO_flux+Depth~Cruise+Habitat+Region+Station, data=do_fx, FUN=c(mean, sd, length))


ggplot(do_fx_summary, aes(x = Station, y = In_situ_DO_flux.mean, fill=Habitat))+
  geom_bar(stat = "identity")+
  geom_errorbar(aes(x=Station, ymin=In_situ_DO_flux.mean-In_situ_DO_flux.sd, ymax=In_situ_DO_flux.mean, colour=Habitat))+
  facet_wrap(~Cruise, scale="free_x")+
  ylab(expression(Oyxgen~flux~(mmol~m^-2~day^-1)))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) #%+replace% dark

# Fit a log-linear model
f <- aov(log10(-In_situ_DO_flux.mean)~Depth.mean*Habitat*Region, data=subset(do_fx_summary, !(Region=="Dongsha"|Region=="Taiping")))
summary(f)
TukeyHSD(f, "Region")

ls <- splitBy(~Habitat, data=do_fx_summary)
f<-lapply(ls, FUN=function(x)lm(log10(-In_situ_DO_flux.mean)~Depth.mean, data=x))
lapply(f, FUN=summary)
nd <- lapply(ls, FUN=function(x){
  out <- as.data.frame(seq(min(x$Depth.mean), max(x$Depth.mean)))
  names(out) <- "Depth.mean"
  return(out)
})

fnd <- list(Canyon=list(f=f[[1]], nd=nd[[1]]), Slope=list(f=f[[2]], nd=nd[[2]]))
pred <- lapply(fnd, FUN=function(x)cbind(x$nd, -10^predict(x$f, x$nd, interval="confidence")))
pred <- ldply(pred, rbind)
names(pred)[1] <- "Habitat"

ggplot()+
  geom_point(data=do_fx_summary, aes(x = Depth.mean, y = In_situ_DO_flux.mean, colour=Habitat, shape=Region), size=3)+
  scale_shape_manual(values=c(19, 3, 4, 1, 0))+
  geom_errorbar(data=do_fx_summary, aes(x=Depth.mean, ymin=In_situ_DO_flux.mean-In_situ_DO_flux.sd, ymax=In_situ_DO_flux.mean+In_situ_DO_flux.sd, colour=Habitat))+
  geom_line(data=pred, aes(x=Depth.mean, y=fit, colour=Habitat))+
  geom_ribbon(data=pred, aes(x=Depth.mean, y=fit, ymin=lwr, ymax=upr, fill=Habitat), alpha=0.2)+
  facet_wrap(~Habitat, scales="free")+
  xlab("Depth (m)")+
  ylab(expression(Oyxgen~flux~(mmol~m^-2~day^-1)))+
  theme_bw() #%+replace% dark

ggplot(data=do_fx_summary, 
       aes(x = Depth.mean, y = -In_situ_DO_flux.mean,
           ymin=-In_situ_DO_flux.mean-In_situ_DO_flux.sd,
           ymax=-In_situ_DO_flux.mean+In_situ_DO_flux.sd,
           colour=Habitat, fill=Habitat, group=Habitat, shape=Region))+
  geom_point(size=3)+
  scale_shape_manual(values=c(19, 3, 4, 1, 0))+
  scale_y_log10()+
  geom_errorbar()+
  stat_smooth(method="lm", formula=y~x, alpha=0.2)+
  facet_wrap(~Habitat, scales="free")+
  xlab("Depth (m)")+
  ylab(expression(Total~Oyxgen~Utilization~(mmol~m^-2~day^-1)))+
  theme_bw() #%+replace% dark

ggplot(data=do_fx_summary)+
  geom_point(size=3, aes(x = Depth.mean, y = -In_situ_DO_flux.mean, colour=Habitat, shape=Region))+
  scale_shape_manual(values=c(19, 3, 4, 1, 0))+
  scale_y_log10()+
  geom_errorbar(aes(x = Depth.mean, y = -In_situ_DO_flux.mean,
           ymin=-In_situ_DO_flux.mean-In_situ_DO_flux.sd,
           ymax=-In_situ_DO_flux.mean+In_situ_DO_flux.sd, colour=Habitat))+
  stat_smooth(method="lm", formula=y~x, alpha=0.2, colour="gray", aes(x = Depth.mean, y = -In_situ_DO_flux.mean))+
  xlab("Depth (m)")+
  ylab(expression(Total~Oyxgen~Utilization~(mmol~m^-2~day^-1)))+
  theme_bw() #%+replace% dark

summaryBy(In_situ_DO_flux.mean~Habitat, data=do_fx_summary, FUN=c(mean, sd, length))

```


Average in-situ carbon flux
---
```{r}
ggplot(do_fx_summary, aes(x = Station, y = In_situ_DO_flux.mean*(-1)*12, fill=Habitat))+
  geom_bar(stat = "identity")+
  geom_errorbar(aes(x=Station, y=In_situ_DO_flux.mean*(-1)*12, ymax=In_situ_DO_flux.mean*(-1)*12+In_situ_DO_flux.sd*(1)*12, ymin=In_situ_DO_flux.mean*(-1)*12, colour=Habitat))+
  facet_wrap(~Cruise, scale="free_x")+
  ylab(expression(Carbon~flux~(mg~C~m^-2~day^-1)))+
  #labs(title="Sediment Community Carbon Remineralization Rate")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) #%+replace% dark

do_fx_summary$DO_flux <- do_fx_summary$In_situ_DO_flux.mean
do_fx_summary$C_flux <- do_fx_summary$In_situ_DO_flux.mean*(-1)*12
do_fx_summary$DO_flux_sd <- do_fx_summary$In_situ_DO_flux.sd
do_fx_summary$C_flux_sd <- do_fx_summary$In_situ_DO_flux.sd*(1)*12
long <- melt(do_fx_summary, measure.vars = c("DO_flux", "C_flux"))
long2 <- melt(do_fx_summary, measure.vars=c("DO_flux_sd", "C_flux_sd"))
long$value_sd <- long2$value
long$variable

pred$variable <- "DO_flux"
pred2 <- pred
pred2[, 3:5] <- pred2[, 3:5]*(-1)*12
pred2$variable <- "C_flux"
pred_comb <- rbind(pred, pred2)
pred_comb$variable <- factor(pred_comb$variable, levels=c("DO_flux", "C_flux"))

ggplot(data=long, aes(x=Depth.mean, y=value))+
  geom_point(size=3, aes(colour=Habitat, shape=Region))+
  scale_shape_manual(values=c(19, 3, 4, 1, 0))+
  geom_errorbar(aes(x=Depth.mean, y=value, ymin=value-value_sd, ymax=value+value_sd, colour=Habitat))+
  geom_line(data=pred_comb, aes(x=Depth.mean, y=fit, colour=Habitat))+
  geom_ribbon(data=pred_comb, aes(x=Depth.mean, y=fit, ymin=lwr, ymax=upr,fill=Habitat), alpha=0.2)+
  facet_wrap(~variable, scale="free_y")+
  xlab("Depth (m)")+
  ylab(expression(Flux~(mmol~Oxygen~m^-2~day^-1)~or~(mg~Carbon~m^-2~day^-1)))+
  #labs(title="Sediment Community Oxygen Consumption Rate")+
  theme_bw() #%+replace% dark
```

```{r}
station_mean <- summaryBy(DO_flux+C_flux+In_situ_DO_flux.length+Depth.mean~Region+Habitat+Station, data=do_fx_summary, FUN=c(mean, sd, length, sum))
station_mean <- station_mean[, c("Region", "Habitat", "Station", "Depth.mean.mean", "DO_flux.mean", "DO_flux.sd", "C_flux.mean", "C_flux.sd", "DO_flux.length", "In_situ_DO_flux.length.sum")]
names(station_mean) <- c("Region", "Habitat", "Station", "Depth", "DO_flux.mean", "DO_flux.sd", "C_flux.mean", "C_flux.sd", "# of cruise", "# of incubation")

lev <- c("SC2", "SC3","KS1", "KS3",
         "GC1", "GC2", "GC3", "GC4", "GC5", "GC6",
         "S1", "S2", "S3", "S4", "S5", "S6", "S7", "GS1", "GS2", "GS3", "GS4", "GS5", "GS6", "GS7","M1", "L1",
         "FC1", "FC2", "FC4", "FC5A","FS1", "FS2", "FS5C",
         "ST1", "ST3", "ST5", "ST5-2")

station_mean$Station <- factor(station_mean$Station, levels = lev)
station_mean$Region <- factor(station_mean$Region, levels = c("Kaohsiung", "Gaoping", "Fangliao", "Dongsha", "Taiping"))

cord <- coordinates(loc)[match(station_mean$Station, loc$Station),]
kable(cbind(cord, station_mean), align="c")
```

```{r, fig.width=12, fig.height=6}
library(cowplot)

p1 <- ggplot(station_mean, 
       aes(x = Station, y = DO_flux.mean, ymin=DO_flux.mean-DO_flux.sd, ymax=DO_flux.mean, colour=Habitat, fill=Habitat))+
  geom_bar(stat = "identity")+
  geom_errorbar()+
  ylab(expression(Oyxgen~flux~(mmol~m^-2~day^-1)))+
  scale_y_reverse()+
  #labs(title="Sediment Community Carbon Remineralization Rate")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) #%+replace% dark

p2 <- ggplot(station_mean, 
       aes(x = Station, y = C_flux.mean, ymax=C_flux.mean+C_flux.sd, ymin=C_flux.mean, colour=Habitat, fill=Habitat))+
  geom_bar(stat = "identity")+
  geom_errorbar()+
  ylab(expression(Carbon~flux~(mg~C~m^-2~day^-1)))+
  #labs(title="Sediment Community Carbon Remineralization Rate")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) #%+replace% dark

plot_grid(p1, p2, ncol=1, align = "h", axis="b")
```

# Match SCOC to environmental data
```{r, fig.width=10, fig.height=8, eval=FALSE}
# CTD data
ctd <- as.data.frame(read_excel("../GPSC_data/GPSC_CTD/GPSC_CTD_2021.08.15.xlsx", sheet=1))
ctd <- splitBy(~Cruise+Station, ctd)

# Function to get average of bottom 3 deepest CTD data
deep_fun <- function(x) {
   dat <- x[order(x$pressure, decreasing=TRUE)[1:3],]
   summaryBy(.~Cruise+Station, data=dat, keep.names=TRUE, na.rm=TRUE)
}

ctd <- lapply(ctd, FUN=deep_fun)
ctd <- ldply(ctd)[, -1]
ctd$transmissometer[ctd$transmissometer<=0] <- 0 # Set negtive transmissometer to zero

# Average temperature, sigma_theta and density
ctd$Temperature <- rowMeans(ctd[, c("temperature_T1", "temperature_T2")], na.rm=TRUE)
ctd$Salinity <- rowMeans(ctd[, c("salinity_T1C1", "salinity_T2C2")], na.rm=TRUE)
ctd$Sigma_theta <- rowMeans(ctd[, c("density_T1C1...11", "density_T2C2...12")], na.rm=TRUE)
ctd$Density <- rowMeans(ctd[, c("density_T1C1...13", "density_T2C2...14")], na.rm=TRUE)

id1 <- with(ctd, paste(Cruise, Station))
id2 <- with(do_fx, paste(Cruise, Station))
# Fill station with no CTD data
id2[id2=="OR1_1190 FC2A"] <- "OR1_1190 FC2"
id2[id2=="OR1_1190 GS6"] <- "OR1_1138 GS6"
ctd <- ctd[match(id2, id1), ]
head(ctd)

# Sediment data
col_types <- c(rep("text", 2), "numeric", "text", rep("numeric", 16))
sed <- as.data.frame(read_excel("../GPSC_data/GPSC_sediment/GPSC_sediment_2021.06.21.xlsx", sheet=1, col_types=col_types))
sed <- sed[sed$Section=="0-1"|sed$Section=="0-1.5",]

id1 <- with(sed, paste(Cruise, Station))
id2 <- with(do_fx, paste(Cruise, Station))
# Fill station with no CTD data
id2[id2=="OR1_1190 FS5C"] <- "OR1_1190 FS5B"
sed <- sed[match(id2, id1), ]

# Profiling data
fx <- read.csv("../GPSC_data/GPSC_o2_profile/GPSC_DOU.csv")
fx <- summaryBy(Integrated_Prod~Cruise+Station, data=fx, keep.names=TRUE)
id1 <- with(fx, paste(Cruise, Station))
id2 <- with(do_fx, paste(Cruise, Station))
fx <- fx[match(id2, id1), ]

# Prokaryote data
bac <- read_excel("../GPSC_data/GPSC_bact/GPSC_bacteria_count_OR1-1190.xlsx", sheet=1, skip=1, n_max=10)[,-1]
bac <- melt(bac)
bac$Bac_abun <- bac$value*133884.298
fro <- ldply(strsplit(as.character(bac$variable), split="-"))
names(fro) <- c("Station", "Deployment", "Tube")
bac <- cbind(fro, bac)
bac$Cruise <- "OR1_1190"
# Convert to biomass (ug ml-1) (assuming 10 fgC cell-1, Deming & Capenter 2008)
bac$Bac_biom <- bac$Bac_abun*10/1E6
bac <- summaryBy(Bac_abun+Bac_biom~Cruise+Station, data=bac, keep.names=TRUE)
id1 <- with(bac, paste(Cruise, Station))
id2 <- with(do_fx, paste(Cruise, Station))
bac <- bac[match(id2, id1), ]

# Macrofauna
# Biomass
col_types <- c("text", "text", "text", "numeric", "numeric", "text", "text", "text", "text", "text", "text", 
              "numeric", "numeric", "numeric", "numeric", "numeric", "text")
mac <- NULL
for(i in 1:15){
  d <- read_excel("../GPSC_data/GPSC_macro_size/GPSC_macro_size_2019.04.30.xlsx", sheet=i, col_types=col_types)
  mac <- rbind(mac, d)
}
mac <- as.data.frame(mac)
mac <- subset(mac, Size<100)
mac <- summaryBy(Size~Region+Habitat+Cruise+Station+Deployment+Tube, data=mac, FUN=sum)
mac$log10_Mac_biom <- log10(mac$Size.sum*1.13/0.008659015)
id1 <- with(mac, paste(Cruise, Station, Tube))
id2 <- with(do_fx, paste(Cruise, Station, Tube))
mac <- mac[match(id2, id1), ]
# Density
bio <- read.csv("../GPSC_PRIMER/Macro_taxa_by_site.csv")
id1 <- with(bio, paste(Cruise, Station, Tube))
id2 <- with(do_fx, paste(Cruise, Station, Tube))
mac$log10_Mac_abun <- log10(rowSums(bio[,2:33])/0.008659015)[match(id2, id1)]

# Combine environmental data
env <- cbind(ctd[, c("pressure", "Temperature", "Salinity", "Sigma_theta", "Density", "Oxygen", "fluorometer" , "transmissometer")],
             DOU=fx$Integrated_Prod*864,
             bac[, c("Bac_abun", "Bac_biom")],
             mac[, c("log10_Mac_abun", "log10_Mac_biom")],
             sed[, c("Clay", "Silt", "Sand", "CN", "TOC", "TN", "WC", "WW", "DW")]
             )
row.names(env) <- row.names(do_fx)

# Calculate porosity
# Pore space volume using pore water mass bottom water density
# Fill in seawater desnity for sites not having CTD data 
library(seacarb)

dens <- env$Density
vp <- (env$WW-env$DW)/(dens/1000)
# Dry sediment volume assuming density of 2.65 g/cm3 
vb <- env$DW/2.65
env$Porosity <- vp/(vp+vb)

long <- melt(cbind(do_fx, env), id.vars=c("In_situ_DO_flux", "Habitat"), measure.vars = c("Depth", "Temperature", "Salinity", "Density", "Oxygen", "fluorometer", "transmissometer", "Bac_biom", "log10_Mac_abun", "log10_Mac_biom", "Clay", "Silt", "Sand", "CN", "TOC", "TN"))

p <- lapply(splitBy(~variable+Habitat, long), FUN=function(x)cor.test(-x$In_situ_DO_flux, x$value)$p.value) %>% unlist()

long2 <- ldply(splitBy(~variable+Habitat, long)[p<0.05])

ggplot(data=long, aes(x=value, y=-In_situ_DO_flux, colour=Habitat))+
  geom_point()+
  stat_smooth(data=long2, formula=y~x, method="lm", se=FALSE)+
  facet_wrap(~variable, scales="free_x")+
  scale_y_log10()+
  xlab("")+
  ylab(expression(Total~Oyxgen~Utilization~(mmol~m^-2~day^-1)))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) %+replace% dark
```

